---
title: "AA assignment 1"
author: "Dom Dosmann"
date: "2025-02-02"
output: pdf_document
---
## Install packages and libraries
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

install.packages(c("tidyverse", "ggplot2", "summarytools"))

library(tidyverse)  
library(ggplot2)  
library(summarytools) 

```


## Import Data Set
```{r}
Netflix <- read.csv("netflix_titles.csv")
```
# The data is about Netflix movies and tv shows and when they are released, who is starred in them, who directs it and a couple other categories. I found out because of this dataset that each show and movie has its own unique ID. Another thing I found interesting was how many ratings there are on shows because I wanted to make a graph on the amount of each rating but couldn't because there were too many ratings to fit on a graph. The part I struggled with the most was figuring out a graph I could use since the dataset has a length of 8,807.

## Quick Analysis
```{r}
colnames(Netflix)
```
# By using the colnames I am able to figure out all of the 12 column titles and represent what the dataset is more about without using all 8000 variables in the dataset.
```{r}
summary(Netflix)
```
# using summary I am able to crasp wether the variables are categorical, integers, or numeric. 
```{r}
head(Netflix)
```

```{r}
tail(Netflix)
```
# Head and tail command show what a couple of the rows of data look like.  

## Tables
```{r pressure, echo=FALSE}
# Bar plot for a single categorical variable
ggplot(Netflix, aes(x = factor(type))) + 
  geom_bar(fill = "blue", color = "black") +
  labs(title = "Freuquency of entertainment type", x = "Type", y = "Amount") +
  theme_minimal()

```
# This graph shows the amount of movies and Tv shows that have been released to netflix. 